Planar Maximal Covering with Ellipses

### 2019-05-04 quali/quali.presentation/slides.tex
wip

%\usepgfplotslibrary{external}
%\tikzexternalize

@@

\centering Thanks to CAPES
\end{frame}

@@

\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Minimum Cover Problem
		\item Maximal Covering Problem
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm
	\end{itemize}
\end{itemize}

@@

\begin{frame}{Preliminaries}

	\begin{block}{Norms}
		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
		\begin{itemize}
			\item Euclidean
			\begin{equation*}
			||u||_2 = \sqrt{u^Tu}
			\end{equation*}

			\item Elliptical
			\begin{equation*}
			||u||_{Q} = \sqrt{u^TQu}
			\end{equation*}
		\end{itemize}
	\end{block}

\begin{frame}{Preliminaries}
	\begin{figure}[H]
		\centering

		\caption{The elliptical and euclidean norms.}
		\input{figures/elliptical.and.euclidean.norms.tex}
		\source{Elaborated by the author.}
		\label{fig:3ellipses_intersect}

\begin{frame}{Preliminaries}

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and a $2x2$ p.d. matrix $Q$, an ellipse is the set of points that satisfy

		\begin{equation*}
		||u-c||_Q = 1,
		\end{equation*}

@@

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
		\item $D(q)$ is a unit disk with center at point $q$
		\item \cite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
		\item \cite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

@@

	\begin{itemize}
		\item In \cite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.

		\item In \cite{zhou} a heuristic method using an algorithm called mean-shift was developed. The mean-shift algorithm converges to a local density maxima of any probability distribution and it is used to find a smaller candidate list of centers for the disks.
	\end{itemize}

@@

@@

\section{Maximal Covering by Ellipses}

@@

	\begin{itemize}
		\item $\E$ is a set of $m$ ellipses
		\item \cite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
		\item \cite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
	\end{itemize}
\end{frame}

@@

@@

		\item Simpler than the $m$ disks algorithm proposed by \cite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).

@@

\begin{frame}{Future Work}
	Primary goals:
\begin{itemize}
	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

	\item Develop an exact method for the version of the problem introduced in \cite{andreta} where the ellipses can be freely rotated.
\end{itemize}
\end{frame}

@@

	\item Develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse. The case with more than one ellipse is left as a challenge for us for the next steps of our research.

	\item In \cite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity. We want to generalize this for the elliptical distance function and achieve a better run-time complexity. We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.

@@

\begin{frame}[allowframebreaks]
	\frametitle{References}
	\bibliographystyle{amsalpha}
	\bibliography{../references.bib}
\end{frame}

>>>>

%\usepgfplotslibrary{external}
%\tikzexternalize
%\usepackage{natbib}

\usepackage[
backend=biber,style=authoryear,autocite=inline
]{biblatex}
%\DeclareLanguageMapping{english}{english-apa}

\addbibresource{../references.bib} %Imports bibliography file
%\DeclareLanguageMapping{american}{american-apa}

@@

\centering Agradecimentos à CAPES.
\end{frame}

@@

\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Minimum Cover Problem
		\item Maximal Covering Problem \autocite{church:1974}
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm
	\end{itemize}
\end{itemize}

@@

%\begin{frame}{Preliminaries}

%	\begin{block}{Norms}
%		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
%		\begin{itemize}
%			\item Euclidean
%			\begin{equation*}
%			||u||_2 = \sqrt{u^Tu}
%			\end{equation*}
%			
%			\item Elliptical
%			\begin{equation*}
%			||u||_{Q} = \sqrt{u^TQu}
%			\end{equation*}
%		\end{itemize}
%	\end{block}

%\end{frame}

@@

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
		\item $D(q)$ is a unit disk with center at point $q$
		\item \autocite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
		\item \autocite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

@@

	\begin{itemize}
		\item In \autocite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.

		\item In \autocite{zhou} a heuristic method using an algorithm called mean-shift was developed. The mean-shift algorithm converges to a local density maxima of any probability distribution and it is used to find a smaller candidate list of centers for the disks.
	\end{itemize}

@@

\end{frame}
\section{Maximal Covering by Ellipses}

\begin{frame}{Ellipses}

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and $Q \in \R^ {2x2}$, an ellipse is the set of points that satisfy

		\begin{equation*}
		||u-c||_Q^2 = (u-c)^TQ(u-c) = 1,
		\end{equation*}

@@

\begin{frame}{Ellipses}
	\begin{figure}[H]
		\centering

		\caption{The ellipse seen as just a linear transformation of a circle.}
		\input{figures/elliptical.and.euclidean.norms.tex}
		\source{Elaborated by the author.}
		\label{fig:3ellipses_intersect}

@@

	\begin{itemize}
		\item $\E$ is a set of $m$ ellipses
		\item \autocite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
		\item \autocite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\begin{figure}
		\caption{Optimal solution with two ellipses for a random instance.}
		\input{figures/example_2_ellipses.tex}
		\source{Elaborated by the author.}
	\end{figure}
\end{frame}

@@

		\item Simpler than the $m$ disks algorithm proposed by \autocite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).

@@

\begin{frame}{Future Work}
	Primary goals:
\begin{itemize}
	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \autocite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

	\item Develop an exact method for the version of the problem introduced in \autocite{andreta} where the ellipses can be freely rotated.
\end{itemize}
\end{frame}

@@

	\item Develop a probabilistic approximation algorithm based on \autocite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse. The case with more than one ellipse is left as a challenge for us for the next steps of our research.

	\item In \autocite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity. We want to generalize this for the elliptical distance function and achieve a better run-time complexity. We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.

@@

\begin{frame}[allowframebreaks]
%	\frametitle{References}
%\bibliographystyle{authoryear-comp}
%	\bibliography{../references.bib}
\printbibliography
\end{frame}
